Effects of the body force on the evacuation dynamics

### 2019-12-20 paper.tex
modificaciones de redaccion en results bottleneck

Fig. \ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity. The evacuation time was defined as the time until 70\% of the pedestrians left the room. The different markers correspond to different $k$ values ($i.e$ different body force stiffness). The crosses correspond to the Helbing original SFM parameter, the up triangles correspond to the value measured in Ref .. and Increasing the $k$ reduced the evacuation time, squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM). The down triangles correspond to an intermediate value between the empirical value presented in Ref... and the chosen by Helbing in Ref...\\

There is a noticeable difference in the evacuation time depending on the $k$ value of the body force. The higher the $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer the overall speed increases (hence the evacuation time).\\

The Faster-is-Faster (FIF) is the phenomenon in which under certain conditions, increasing the desired velocity yields to a reduction of the evacuation time. The Faster-is-Faster is the opposite effect (the higher $v_d$ the lower the evacuation time).  Notice that the presence of the faster-is-faster (FIF) effect and the faster-is-slower are dependent on the value of $k$. In Fig.~\ref{vd_vs_te} we can see that $k=1.2$~E5 only exhibits FIS effect for $v_d>$2~m/s. $k=1.2$~E6 only shows FIF effect and the explored values of $k$ that satisfy $k \leq 6$~E4 exhibit both the FIS and the FIF effect. \\

@@

Fig.~\ref{degree_vd} shows the mean degree of the contact graph as a function of the desired velocity. The degree of a node is defined as the amount of edges assigned to the node. This means, the number of pedestrians that are in contact with a given pedestrian. The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole time from the stationary state until the end of the simulation.\\

>>>>

Fig. \ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity. The evacuation time was defined as the time until 70\% of the pedestrians left the room. The different markers correspond to different $k$ values ($i.e$ different body ``stiffness''). The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM). The down triangles correspond to an intermediate value between the empirical value presented in Ref... and the chosen by Helbing in Ref...\\

There is a noticeable difference in the evacuation time depending on the $k$ value of the body force. The higher the $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer, the overall speed increases (hence the evacuation time decreases).\\

The Faster-is-Faster (FIF) is the phenomenon in which under certain conditions, increasing the desired velocity yields to a reduction of the evacuation time. The Faster-is-Faster is the opposite effect (the higher $v_d$ the lower the evacuation time).  Notice that the presence of the Faster-is-Faster (FIF) effect and the Faster-is-Slower are dependent on the value of $k$. In Fig.~\ref{vd_vs_te} we can see that $k=1.2$~E5 only exhibits FIS effect for $v_d>$2~m/s. When $k=1.2$~E6, the evacuation time reduces as $v_d$ increases, meaning that only FIF is reported. The explored values of $k$ that satisfy $k \leq 6$~E4 exhibit both the FIS and the FIF effect depending on the range of desired velocities. Notice that the behavior of the case in which $k = 0$ is very similar to the case in which $k = 1.2$~E4.\\
% se puede discutir que este resultado es importante porque k=1.2E4 es un valor empirico y k=1.2E5 tambien lo es, osea que el FIF podria estar o no estar dependiendo de cual es el verdadero valor de k. Habria que chequear en unidades reducidas como queda.

@@

Fig.~\ref{degree_vd} shows the mean degree of the contact graph as a function of the desired velocity. The degree of a node is defined as the amount of edges assigned to the node. This means, the number of pedestrians that are in physical contact with a given pedestrian. The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole sampled time (from the time the system reaches the stationary state to the end of the simulation).\\
